\section{CHANGELOG\label{sec:changelog}}
\begin{adjustwidth}{0em}{0pt}

	This document, in being heavily cited and used as a handbook and guiding force for entire organizations and the vast majority of currently active initiatives, will be updated regularly based on its usage and the need for it to be further extended, modified, refined, and so on. 

	The versioning of the document shall adhere to the most common form of software versioning, where the major version is followed by a decimal point and a minor version and the minor version is followed by a decimal point and a release or build version (major.minor.build). In this context, major versions shall be released when document-wide reorganization or deprecation is required, minor versions shall be released when sections or appendices are added, removed, or modified in ways that require they be merged, broken apart, or renamed, and builds shall be released when any change is made to the document itself. 

	Furthermore, the date of the release shall be appended to the major.minor.build form, separated by a dash. e.g. 1.0.0-08.31.2018 is the first version, first release, that occurred on August 31st, 2018. Note that this information may always be found in the bottom right-hand corner of every page of this document.

	The source code for the document is written in LaTeX, and the author of the document would request it remain in that format so as to facilitate quick revision and release. 

	\begin{compactitem}

		\item {\bf v1.0.0-08.31.2018}: initial release of document and exposure of proposed framework for process definition and reference modeling. 

	\end{compactitem}

\end{adjustwidth}