\newglossaryentry{acquirer}
{
	name=acquirer,
	description={Stakeholder that acquires or procures a product or service from a supplier, where ``acquirer'' could be one of the following: buyer, customer, owner, purchaser.}
}

\newglossaryentry{acquisition}
{
	name=acquisition,
	description={process of obtaining a system, software product or software service.}
}

\newglossaryentry{activity}
{
	name=activity,
	description={set of cohesive tasks of a process.}
}

\newglossaryentry{agreement}
{
	name=agreement,
	description={mutual acknowledgment of terms and conditions under which a working relationship is conducted.}
}

\newglossaryentry{audit}
{
	name=audit,
	description={independent assessment of software products and processes conducted by an authorized person in order to assess compliance with requirements.}
}



\newglossaryentry{baseline}
{
	name=baseline,
	description={specification or product that has been formally reviewed and agreed upon, that thereafter serves as the basis for further development, and that can be changed only through formal change control procedures.}
}



\newglossaryentry{configuration item}
{
	name=configuration item,
	description={entity within a configuration that satisfies an end use function and that can be uniquely identified at a given reference point.}	
}

\newglossaryentry{contract}
{
	name=contract,
	description={binding agreement between two parties, especially enforceable by law, or a similar internal agreement wholly within an organization.}
}

\newglossaryentry{customer}
{
	name=customer,
	description={organization or person that receives a product or service.}
}



\newglossaryentry{developer}
{
	name=developer,
	description={organization that performs development tasks (including requirements analysis, design, testing through acceptance) during a life cycle process.}
}



\newglossaryentry{enabling system}
{
	name=enabling system,
	description={system that supports a system-of-interest during its life cycle stages but does not necessarily contribute directly to its function during operation.}
}

\newglossaryentry{evaluation}
{
	name=evaluation,
	description={systematic determination of the extent to which an entity meets its specified criteria.}
}



\newglossaryentry{facility}
{
	name=facility,
	description={physical means or equipment for facilitating the performance of an action, e.g. buildings, instruments, tools.}
}

\newglossaryentry{firmware}
{
	name=firmware,
	description={combination of a hardware device and computer instructions or computer data that reside as read-only software on the hardware device.}
}



\newglossaryentry{implementer}
{
	name=implementer,
	description={organization that performs implementation tasks.}
}



\newglossaryentry{life cycle}
{
	name=life cycle,
	description={evolution of a system, product, service, project or other human-made entity from conception through retirement.}
}

\newglossaryentry{life cycle model}
{
	name=life cycle model,
	description={framework of processes and activities concerned with the life cycle that may be organized into stages, which also acts as a common reference for communication and understanding.}
}



\newglossaryentry{maintainer}
{
	name=maintainer,
	description={organization that performs maintenance activities.}
}

\newglossaryentry{monitoring}
{
	name=monitoring,
	description={examination of the status of the activities of a supplier and of their results by the acquirer or a third party.}
}



\newglossaryentry{non-deliverable item}
{
	name=non-deliverable item,
	description={hardware or software product that is not required to be delivered under the contract but may be employed in the development of a software product.}
}



\newglossaryentry{off-the-shelf}
{
	name=off-the-shelf,
	description={product that is already developed and available.}
}

\newglossaryentry{operator}
{
	name=operator,
	description={entity that performs the operation of a system.}
}

\newglossaryentry{organization}
{
	name=organization,
	description={person or a group of people and facilities with an arrangement of responsibilities, authorities and relationships.}
}



\newglossaryentry{party}
{
	name=party,
	description={organization entering into a contract.}
}

\newglossaryentry{process}
{
	name=process,
	description={set of interrelated or interacting activities which transforms inputs into outputs.}
}

\newglossaryentry{process purpose}
{
	name=process purpose,
	description={high level objective of performing the process and the likely outcomes of effective implementation of the process.}
}

\newglossaryentry{process outcome}
{
	name=process outcome,
	description={observable result of the successful achievement of the process purpose.}
}

\newglossaryentry{product}
{
	name=product,
	description={result of a process.}
}

\newglossaryentry{project}
{
	name=project,
	description={endeavor with defined start and finish dates undertaken to create a product or service in accordance with specified resources and requirements.}
}

\newglossaryentry{project portfolio}
{
	name=project portfolio,
	description={collection of projects that addresses the strategic objectives of the organization.}
}



\newglossaryentry{qualification}
{
	name=qualification,
	description={process of demonstrating whether an entity is capable of fulfilling specified requirements.}
}

\newglossaryentry{qualification requirement}
{
	name=qualification requirement,
	description={set of criteria or conditions that have to be met in order to qualify a software product as complying with its specifications and being ready for use in its target environment or integration with its containing system.}
}

\newglossaryentry{qualification testing}
{
	name=qualification testing,
	description={testing, conducted by the developer and witnessed by the acquirer (as appropriate), to demonstrate that a software product meets its specifications and is ready for use in its target environment or integration with its containing system.}
}

\newglossaryentry{quality assurance}
{
	name=quality assurance,
	description={all the planned and systematic activities implemented within the quality system, and demonstrated as needed, to provide adequate confidence that an entity will fulfill requirements for quality.}
}



\newglossaryentry{release}
{
	name=release,
	description={particular version of a configuration item that is made available for a specific purpose (for example, test release).}
}

\newglossaryentry{request for proposal}
{
	name=request for proposal,
	description={document used by the acquirer as the means to announce its intention to potential bidders to acquire a specified system, software product or software service.}
}

\newglossaryentry{resource}
{
	name=resource,
	description={asset that is utilized or consumed during the execution of a process}
}

\newglossaryentry{retirement}
{
	name=retirement,
	description={withdrawal of active support by the operation and maintenance organization, partial or total replacement by a new system, or installation of an upgraded system.}
}



\newglossaryentry{security}
{
	name=security,
	description={protection of information and data so that unauthorized persons or systems cannot read or modify them and authorized persons or systems are not denied access to them.}
}

\newglossaryentry{service}
{
	name=service,
	description={performance of activities, work, or duties associated with a product.}
}

\newglossaryentry{software item}
{
	name=software item,
	description={source code, object code, control code, control data, or a collection of these items.}
}

\newglossaryentry{software product}
{
	name=software product,
	description={set of computer programs, procedures, and possibly associated documentation and data.}
}

\newglossaryentry{software unit}
{
	name=software unit,
	description={separately compilable piece of code.}
}

\newglossaryentry{stage}
{
	name=stage,
	description={period within the life cycle of an entity that relates to the state of its description or realization.}
}

\newglossaryentry{stakeholder}
{
	name=stakeholder,
	description={individual or organization having a right, share, claim or interest in a system or in its possession of characteristics that meet their needs and expectations.}
}

\newglossaryentry{statement of work}
{
	name=statement of work,
	description={document used by the acquirer as the means to describe and specify the tasks to be performed under the Contract.}
}

\newglossaryentry{supplier}
{
	name=supplier,
	description={organization or individual that enters into an agreement with the acquirer for the supply of a product or service.}
}

\newglossaryentry{system}
{
	name=system,
	description={combination of interacting elements organized to achieve one or more stated purposes.}
}

\newglossaryentry{system element}
{
	name=system element,
	description={member of a set of elements that constitutes a system.}
}



\newglossaryentry{task}
{
	name=task,
	description={requirement, recommendation, or permissible action, intended to contribute to the achievement of one or more outcomes of a process.}
}

\newglossaryentry{test coverage}
{
	name=test coverage,
	description={extent to which the test cases test the requirements for the system or software product.}
}

\newglossaryentry{testability}
{
	name=testability,
	description={extent to which an objective and feasible test can be designed to determine whether a requirement is met.}
}



\newglossaryentry{user}
{
	name=user,
	description={individual or group that benefits from a system during its utilization}
}



\newglossaryentry{validation}
{
	name=validation,
	description={confirmation, through the provision of objective evidence, that the requirements for a specific intended use or application have been fulfilled.}
}

\newglossaryentry{verification}
{
	name=verification,
	description={confirmation, through the provision of objective evidence, that specified requirements have been fulfilled.}
}

\newglossaryentry{version}
{
	name=version,
	description={identified instance of an item.}
}